\section{Grasping}
\label{sec:grasping}

Once the target object is detected, the object frame is obtained from our vision system. In order to grasp the object, since our PR2 is equipped with parallel grippers, we need to decide from which position and in which direction the gripper is going to approach the object. For this, we always project the object frame based on the bin frame such that the X axis of the object frame points inwards the shelf, and the Z axis points downwards. Note that in order to ensure that the object can be approached without collision, we labeled all objects in offline so that the X axis returned from the vision system can be always approached, i.e. the gripper is wide enough to grasp the corresponding side. Thereafter, similarly to the grasping stages in \cite{hang2016b}, our grasping system works in the following steps:
\begin{itemize}
 \item \textbf{Pre-grasping:} The gripper is posed in front of the bin and aligned in X axis of object frame, the gripper's opening direction is aligned in the XY plane of object frame.
 \item \textbf{Approaching:} The gripper approaches the object in X direction until a pre-determined depth in the object frame is reached.
 \item \textbf{Grasping and lifting:} The gripper closes and lifts the object to a pre-determined height. At this point, we read the gripper's joint angle to check whether the object is grasped. If not, the system will return failure and give control back to the behavior tree. Otherwise, it returns success and continue to the next step.
 \item \textbf{Post-grasping:} When the object is grasped, it is not trivial to plan a motion to move the arm out of the shelf, especially for large objects. Therefore, we first move the object to the bin center, and then move the whole robot backwards. Once the object is out of the shelf, the robot go to the order bin and put the object into it.
\end{itemize}
In cases when the target object is very small, e.g., tennis ball and duck toy etc., the approaching procedure shown above is not able to reach the object due to the collision with the bin bottom. In those cases, our system will first try to approach the above area of the object, and then move downwards to reach the desired grasping pose. It is worthwhile noticing that, dividing the grasping motion into steps significantly increased the success rate for MoveIt! to find solutions within a short time limitation, since the above steps efficiently guides the motion planner through narrow passages posed by the small bin areas. 
